---
title: "433 homework 3"
author: "Yufeng Han"
date: "2021/9/24"
output: html_document
---

##GitHub email : 972525414@qq.com


## How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r}
library(nycflights13)
library(tidyverse)
summary(flights)
```
 8255 flights have a missing dep_time, 8713 flights have a missing arr_time,2359 flights have a missing sched_arr_time,9430 have a missing arr_delay. There rows may records aircraft that for some reason could not take off properly or were delayed, because the departure time could not be confirmed so the arrival time was missing or delayed. Some of the reasons are because the plane may have been left in the ocean with no way to collect data.


##Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
 new_dep_time = (flights$dep_time %/% 100) *60 + flights$dep_time %% 100
 new_sched_dep_time= (flights$sched_dep_time %/% 100) *60 + flights$sched_dep_time %% 100
 


```

```{r}
flights %>%
  mutate(dep_date = lubridate::make_datetime(year, month, day)) %>%
  group_by(dep_date) %>%
  summarise(cancelled = sum(is.na(dep_delay)), 
            n = n(),
            mean_dep_delay = mean(dep_delay,na.rm=TRUE),
            mean_arr_delay = mean(arr_delay,na.rm=TRUE)) %>%
    ggplot(aes(x= cancelled/n)) + 
    geom_point(aes(y=mean_dep_delay), colour='blue', alpha=0.5) + 
    geom_point(aes(y=mean_arr_delay), colour='red', alpha=0.5) + 
    ylab('mean delay (minutes)')
```

